Hemodynamic responses of the anterior "parahippocampal place area" (PPA) to a Hollywood movie's audio-description

### 2020-11-19 paper/main.tex
shorten Aminoff 2015

\citep{baumann2016functional} zu \citep{aminoff2015associative}:
% pPHC
pPHC showed increased activity when participants viewed (alrady familiar)
spatial configurations of meaningless shapes (regardless of their individual
identities);
% aPHC
aPHC was more active during the display of (already familiar) meaningless shapes
(regardless of their spatial configuration).
%
These findings can be interpreted as suggestive of pPHC visuospatial processes
and aPHC contextual processes \citep{baumann2016functional}.

@@

\citep{aminoff2015associative} How are complex visual entities such as scenes
represented in the human brain? Along what visual and semantic dimensions are
scenes encoded in memory?
%
One hypothesis: global spatial properties provide a basis for categorizing the
neural response patterns arising from scenes \citep{aminoff2015associative}.
%
In contrast, non-spatial properties, such as single objects, also account for
variance in neural responses\citep{aminoff2015associative}.

%
The list of critical scene dimensions has continued to grow (sometimes in a
contradictory manner), coming to encompass properties such as geometric layout,
big/small, crowded/sparse, and
three-dimensionality\citep{aminoff2015associative}.
%
We demonstrate that these dimensions may be better understood within the more
general framework of associative properties\citep{aminoff2015associative}.
%
Across both the perceptual and semantic domains, features of scene
representations are related to one another through learned
associations\citep{aminoff2015associative}.

%
We investigated whether different types of relations, all falling under the
heading of associative processing, reliably recruit specific components of the
network of brain regions known to be scene
selective\citep{aminoff2015associative}.
%
Critically, the components of such associations are consistent with the
dimensions that are typically invoked to account for scene understanding and its
neural bases\citep{aminoff2015associative}.

Results: We show that non-scene stimuli displaying novel associations across
identities or locations recruit putatively scene-selective regions of the human
brain (the parahippocampal/lingual region, the retrosplenial complex, and the
transverse occipital sulcus/occipital place area)\citep{aminoff2015associative}.
%
Moreover, we find that the voxel-wise neural patterns arising from these
associations are significantly correlated with the neural patterns arising from
everyday scenes providing evidence whether the same encoding principals underlie
both types of processing\citep{aminoff2015associative}.

%
Interpretation: Results provide evidence for the hypothesis that the neural
representation of scenes is better understood within the broader theoretical
framework of associative processing\citep{aminoff2015associative}.
%
Results also demonstrate a division of labor that arises across scene-selective
regions when processing associations and scenes providing better understanding
of the functional roles of each region within the cortical network that mediates
scene processing\citep{aminoff2015associative}.

@@

Scenes are complex stimuli containing rich, statistically regular information
about objects, background, context, semantics, and spatial layout at multiple
scales\citep{aminoff2015associative}.
%
As a core component of scene understanding we extract and learn these
regularities (for example, coming to know that certain objects typically appear
together or that certain objects are likely to appear in a given spatial
relationship [1–3])\citep{aminoff2015associative}.
%
Critically, these associated regularities are not only useful in defining scene
categories, but also in predicting which other objects and relations are likely
to occur within a scene [5]\citep{aminoff2015associative}.

% a-modality
Features of any kind of mental representation, irrespective as to whether that
representation is nominally visual, linguistic, etc., are related to one another
via learned associations\citep{aminoff2015associative}.
%
These associations are not necessarily modality-specific (for example, visual
representations are likely to carry many semantic and affective associations not
directly present in the image)\citep{aminoff2015associative}.
%
With respect to scene understanding, we construe contextual associative
processing as a more semantically-driven process in which associations are not
arbitrary relations, but rather relations that emerge as a consequence of their
shared context within the larger scene.
%
Associations are not simply frequently co-occurring features pairs; instead they
are pairs that both co-occur and add meaning to scenes
\citep{aminoff2015associative}.
%
Furthermore, the mechanism by which scenes are perceived, recognized, and
understood, is through means of processing the associations elicited from
components of the scene \citep{aminoff2015associative}.

%
At the core of neurally-based theories of scene perception are the issues of the
computations and representations instantiated in each of these brain regions.
The literature has focused on more on the latter, characterizing the nature of
the information encoded about scenes\citep{aminoff2015associative}.
%
It has been suggested that scenes are analyzed in terms of their spatial global
properties, such as the ‘spatial envelope’, which takes into account a scene’s
overall spatial structure and layout [20,21]\citep{aminoff2015associative}.
%
Empirically, it has been demonstrated that these global properties are salient
cues for categorizing scenes in both behavior [22] and in patterns of neural
activity [23–26]\citep{aminoff2015associative}.
%
Compared to other factors that characterize scenes (i.e., content and
depth), the expanse of the scene (i.e. its spatial boundary) has been found to
be the most effective in accounting for variations in the neural responses
within scene-selective brain regions [23,24]\citep{aminoff2015associative}.
%
Generally, spatial information defining the geometric layout of a scene has
often been implicated in determining the neural responses arising from
scene-selective brain regions [27]\citep{aminoff2015associative}.

%
In contrast, non-spatial properties can account for variations in the neural
responses associated with scene processing and representation\citep{aminoff2015associative}.
%
For example, Harel et al. [11], found that the neural encoding of scenes
captures information about single objects (i.e., non-spatial) as well as
background spatial properties\citep{aminoff2015associative}.
%
Supporting this point, strongly contextualized objects also elicit neural
activity within scene-selective cortex [28,29]\citep{aminoff2015associative}.

%
Finally, objects present as the contents of a scene can also modulate activity
in scene-selective regions\citep{aminoff2015associative}.
%
For example, scenes where the most salient object carries strong contextual
associations (e.g., a scene with a parking meter) recruit scene-selective
regions more than do scenes with a salient object carrying weak contextual asso-
ciations (e.g., a scene with a squirrel) [30]\citep{aminoff2015associative}.
%
Overall, scene-selective brain regions are encoding a rich collection of
information, including global and local properties, spatial background infor-
mation, and individual object tokens\citep{aminoff2015associative}.

%
One concern with the current state of the field is that the list of critical
properties keeps growing (e.g., big/small, crowded/sparse, three-dimensionality
[31–33]), with some theories seemingly contradicting others about which
properties are critical in scene understanding\citep{aminoff2015associative}.
%
We posit that many dimensions of scene understanding may be better understood
within a more general framework in which scenes are encoded with respect to
their associative properties [28,30,34,35]\citep{aminoff2015associative}.
%
Associative properties are not restricted to the spatial or the global domain,
and can account for why information regarding spatial layout and single objects
play an important role in scene understanding and concomitant neural
responses\citep{aminoff2015associative}.
%
Associative processing not only offers an explanation for what particular kinds
of information are present in scene representation (e.g., objects and spatial
information), but also a basis for explaining how and why this information is
important\citep{aminoff2015associative}.
%
For instance, on average, spatial layout and global properties may carry more
associative information, and thus are typically prominent in accounts of the
mechanisms mediating scene recognition\citep{aminoff2015associative}.
%
Consider expanse, a salient, organizing principle within scene representations:
expanse may be construed as a superordinate category strongly associated with
many other properties of a scene, for instance nature, navigating, hiking, and,
therefore, is likely to be strongly predictive of additional scene
information\citep{aminoff2015associative}.

%
To test the idea that associative processing is inherent in scene understanding,
we explore whether the network of brain regions recruited in scene perception is
also recruited when processing non-scene-like stimuli that contain associative
information\citep{aminoff2015associative}.
%
The critical point being that if these regions are active when processing the
associations learned between non-scene-like novel stimuli than these regions
must not be involved in only processing the visual properties of the scene, but
rather, are processing what is associated with the components of the scene as
learned from previous experience\citep{aminoff2015associative}.
%
we focus on the associative processing of concurrent object identities (i.e.,
semantic associations) and spatial relations between objects (i.e., spatial
associations)\citep{aminoff2015associative}.
%
Of course, other domains of associative processing, for example, diagnostic
mid-level features, almost surely play some role as
well\citep{aminoff2015associative}.
%
For both semantic and spatial associations, we predict that the three
typically-identified scene-selective brain areas, the PPA, RSC, and OPA, will
all exhibit selective activity for both scenes and for associations in general,
without necessarily having any obvious “scene-like”
qualities\citep{aminoff2015associative}.

%
We are positing that scene processing is best understood as, at least in part,
arising from a more general mechanism–that of associative
processing\citep{aminoff2015associative}.
%
The fact that this mechanism is more general does not make it vague. Our point
is that learning and encoding relations between tokens (“associations”) is a
fundamental process across many cognitive domains and, critically, this process
has explanatory validity for scene processing\citep{aminoff2015associative}.
%
Reframing scene processing as involving a more general mechanism helps
articulate the means by which scene perception
occurs\citep{aminoff2015associative}.

%
Participants were scanned while they engaged in processing either everyday
scenes or associations between meaningless shapes\citep{aminoff2015associative}.
%
For the latter condition, participants, immediately prior to the scanning
session, performed a task (unrelated to the associations) in which they
implicitly learned spatial or identity associations between configurations of
novel shapes (Fig 1)\citep{aminoff2015associative}.
%
First, to compare brain activity from learning novel associations to the
processing of scenes, we correlated the distributed, voxel-by-voxel pattern of
activities arising from these two conditions, thereby testing whether similar
neural mechanisms mediate both general associative processing and scene
perception\citep{aminoff2015associative}.
%
Second, consistent with previous work ([28,31,34,37]) we asked whether the
neural encoding of scenes shifts across associ- ation types–from non-spatial or
semantic scene properties to spatial scene properties–as one moves from the
anterior to the posterior PPA\citep{aminoff2015associative}.
%
These analyses shed light on the hypothesis that a single underlying
principle, associative processing, accounts for how scenes are represented in
the brain\citep{aminoff2015associative}.

%
Although prior studies have manipulated spatial and identity associations by
having participants learn meaningless patterns of shapes [34], ours is the first
study to directly compare such associative processing with the processing of
everyday scenes\citep{aminoff2015associative}.
%
Moreover, we include two new baselines to better understand whereby effects of
associations arise: weak contextual objects and scrambled images. Finally, we
are careful to collect an additional independent dataset to functionally define
scene-selective regions\citep{aminoff2015associative}.
%
These new conditions are all advances (in terms of explicating the processing of
scene-selection regions) relative to our earlier study in which we used the same
shapes and trained participants over a two-week period [34]\citep{aminoff2015associative}.
%
We also include several methodological changes: training was much briefer; the
task was changed from an explicit task to an implicit task; a spatial-only
associative condition was included to isolate spatial processing independently
of identity associations; and the no-associa- tion condition provides a better
control in that it now shows the same number of shapes as the association
condition (i.e., 3)\citep{aminoff2015associative}.

@@

%
The general principle of associative processing may apply broadly across
scene-selective ROIs. Nevertheless, there is some evidence that within the
parahippocampal region, anterior and posterior regions may support different
kinds of associations [34,37,40,41]\citep{aminoff2015associative}.
%
We posit: aPPA processes non-spatial associations such as those realized in the
ID condition. pPPA process spatial associations such as those realized in the SP
condition\citep{aminoff2015associative}.
%
We tested this hypothesis by examining two contrasts within scene-selective PHC
regions: SP versus NA and ID versus NA\citep{aminoff2015associative}.
%
To identify the appropriate scene-selective ROIs for this analysis, we used the
scenes versus baseline contrast to capture all scene-related activity within
parahippocampal cortex\citep{aminoff2015associative}.
%
Within these subregions, only those voxels that demonstrated significant
scene-related activity from the scenes versus objects/scrambled localizer were
analyzed\citep{aminoff2015associative}.
%
However, observed scene-related activity within the parahippocampal/lingual
region extended beyond the posterior border of the parahippocampal cortex and
into the lingual gyrus\citep{aminoff2015associative}.
%
To capture these responses, we also included these more posterior voxels as the
most posterior subregion, giving us a total of five subregions covering the PPA
from anterior to posterior regions\citep{aminoff2015associative}.

%
Data were analyzed examining both the average activity within each subregion,
and the distributed pattern of activity in each subregion correlated with the
pattern for scenes\citep{aminoff2015associative}.
%
The pattern of average activity across subregions supports a division of labor
in which anterior subregions showed the largest differences in the ID versus NA
contrast relative to the SP versus NA contrast, while posterior subregions
showed the largest differences in the SP versus NA contrast relative to the ID
versus NA contrast\citep{aminoff2015associative}.
%
In the LH PPA this was significant in both in the interaction of Association by
Subregion (F(4,56) = 5.85, p < .001) and critically, in the linear interaction
contrast (F(1,14) = 8.05, p < .01)\citep{aminoff2015associative}.
%
The significance of this linear contrast indicates that the transition from
identity to spatial associative processing may be construed as a gradient from
anterior to posterior regions of parahippocampal cortex. However, the same
Association by Subregion interaction was not observed in the RH PPA\citep{aminoff2015associative}.

%
To examine whether identity and spatial associations also capture
functionally-relevant properties within scenes, we examined the similarity
between the voxel-wise pattern of BOLD responses elicited by identity
associations and real-world scenes, and by spatial associations and real-world
scenes\citep{aminoff2015associative}.
%
We hypothesized that, to the degree that these two types of associations are
intrinsic to scene processing, similar patterns of activation across each of the
two association conditions and real-world scenes would identify those
(potentially separable) neural substrates supporting the representation of these
kinds of associations\citep{aminoff2015associative}.
%
Unthresholded t-values for the ID versus NA and SP versus NA contrasts within
each of the five PPA subregions were ex- tracted for each voxel and then
cross-correlated within each subregion with the real-world scenes versus
objects/scrambled contrast\citep{aminoff2015associative}.
%
In LH PPA the interaction within an omnibus ANOVA [the two factors being
Subregion (moving from the most posterior to the most anteri- or) x Association
(identity or spatial)] was significant (F(4,56) = 2.69, p < .04) as well as the
critical linear x linear trend analysis (F(1,14) = 7.57, p < .016) (Fig 3A)\citep{aminoff2015associative}.
%
Consistent with our analysis of average activity within these subregions, this
interaction was not observed in the RH PPA (F(1,14) = 1.22, n.s.) (S1 Fig)\citep{aminoff2015associative}.
%
However, it is worth noting that within the right hemisphere, the correlation
between spatial associations and real-world scenes did exhibit the predicted
pattern whereby the strongest correlation was observed in posterior subregions
of PPA, with a progressively lower correlation being observed moving in a
posterior to anterior direction (S1 Fig)\citep{aminoff2015associative}.

%
Our results indicate that the organization of PPA with respect to associative
processing is a gradient in which posterior subregions of PPA are biased towards
spatial associations and anterior subregions of PPA are biased towards identity
associations\citep{aminoff2015associative}.
%
Additional support for this claim is shown in Fig 3B, where instead of dividing
the PPA into five equal subregions, the correlation was run over progressively
more and more of the PPA, starting from the most posterior subregion and adding
subregions until the entire PPA was taken into account\citep{aminoff2015associative};
%
As illustrated, the most extreme ends of the PPA show the strongest biases
towards capturing the similarity of either spatial associations and scenes, or
identity associations and scenes \citep{aminoff2015associative}
%
whereas if the whole PPA were to be surveyed, these differences would be masked.
Of note, this gradient appears to be truly continuous across posterior and
anterior portions of the PPA–even considering only the posterior PPA, we observe
a gradient in which the strongest preference for spatial associations is found
in the most posterior portions of the posterior
PPA \citep{aminoff2015associative}.
%
Similarly, considering only the anterior PPA, we observe a gradient in which the
strongest preference for identity associations is found in the most anterior
portions of the anterior PPA \citep{aminoff2015associative}.

@@

 Building on our general results regarding associative processing, our current
 findings also establish some specialization (at least in preference) for the
 processing of associative information across the PPA
 \citep{aminoff2015associative}.
%
pPPA is preferentially recruited by spatial associations while anterior PPA is
preferentially recruited by semantic (i.e., non-spatial) associations
\citep{aminoff2015associative}.
%
A functional distinction between anterior and posterior PPA has been reported
previously. In particular, this distinction has been based on PPA responses when
processing objects associated with spatial contexts (i.e., contexts associated
with specific places, for example, an oven and a kitchen) and when processing
objects associated with non-spatial contexts (i.e., contexts not tied to
specific places, for example, champagne with New Year’s Eve) [28,34,37,40,41]
\citep{aminoff2015associative}.
%
Here we explicitly investigated this spatial/non-spatial distinction by
isolating the two association types in simple, novel stimuli and then relating
these controlled stimuli to the processing of real-world scenes containing
similar associations \citep{aminoff2015associative}.
%
We predicted that this Association-Type x Scene correlation would reveal the
expected posterior to anterior progression with spatial properties within scenes
selectively recruiting posterior PPA and non-spatial, identity properties within
scenes selectively recruiting anterior PPA\citep{aminoff2015associative}.
%
Moreover, we expected that this functional division would be continuous, with
the similarity in BOLD responses elicited by scenes and trained spatial
associations decreasing in a posterior to anterior direction
\citep{aminoff2015associative}.
%
In contrast, the similarity in BOLD responses elicited by scenes and trained
identity associations was predicted to decrease in an anterior to posterior
direction.  These predictions were confirmed in our
study\citep{aminoff2015associative}.

%
This information processing gradient may lie within a broader, more general
organization of the PHG\citep{aminoff2015associative}.
%
The gradient of processing identity or non-spatial associative information may
continue through the neighboring perirhinal cortex, which is thought to be
involved in object and person recognition particularly with regard to combining
different fea- tures of knowledge, such as a stop sign is red
[42]\citep{aminoff2015associative}.
%
In contrast, the pPPA border regions where mid-level visual information is
processed, which may be more sensitive to spatial
information\citep{aminoff2015associative}.
%
We do note, however, that this interaction was only observed in the left
hemisphere, although the right hemisphere demonstrated a similar gradient of
specialization in spatial processing from posterior to
anterior\citep{aminoff2015associative}.
%
However, the activity related to identity processing was less well organized.
This pattern of results is somewhat consistent with the fact that the left
hemisphere is often implicated in more semantically-oriented processing, for
example, scene categorization, whereas the right hemisphere has been implicated
in more spatial processing, for example, as in the visual details between
different exemplars of the same category [10]\citep{aminoff2015associative}.
%
These patterns hint that the right hemisphere PPA may play a larger role in the
processing of the spatial relations within scenes and a lessor role in the
processing of scene semantics\citep{aminoff2015associative}.
%
In sum, our current functional view of the PPA is as a gradient in which
progressively different scene dimensions come to be
instantiated\citep{aminoff2015associative}.

@@

Our results move beyond simply describing which brain regions are selectively
recruited by visual scene processing\citep{aminoff2015associative}.
%
We invoke associative processing as a computationally-definable construct for
predicting the spatial organization of scene-related activity across different
scene properties\citep{aminoff2015associative}.
%
Consequently, we suggest that the neural mediators of scene processing should
not be construed as encapsulated visual modules, but rather as manifestations of
associations that reflect the interaction between visual recognition processes
and the application of long-term memories arising from past experiences (Aminoff
et al., 2013)\citep{aminoff2015associative}.
%
Within this framework, scene processing is not a purely bottom-up visual
process, but rather is an interactive process in which we are constantly
considering–in the form of both spatial and non-spatial associations– our past
experiences to generate predictions, expectations, and constraints about our
physical environment\citep{aminoff2015associative}.

%
More specifically, we suggest that general associative processing mechanisms are
sensitive to frequently occurring or repeated relations within scenes, including
object identities that co- occur, spatial relations between the objects, and
spatial locations for individual objects, all of which facilitate the
recognition and categorization of visual scenes\citep{aminoff2015associative}.
%
As such, the collection of associations that help to define a scene provides a
context for individual elements within that scene\citep{aminoff2015associative}.
%
For example, a towel hanging on a rack near a shower would most likely be a
bathroom towel, whereas the same towel lying flat on the sand near an umbrella
would most likely be a beach towel\citep{aminoff2015associative}.
%
We contend that the parsing of these sorts of contextual associations within
scenes is fundamental to scene understanding, and that scene understanding
construed as such, can then influence cognitive processing in myriad
ways\citep{aminoff2015associative}.

%
Within the human brain, we argue that the neural bases for the application of
contextual knowledge is a functional gradient spanning different types of
associations instantiated across the PPA, and contextually-mediated
representations within the RSC and OPA\citep{aminoff2015associative}.
%
Most saliently, our observations of selectivity for spatial and identity
associations provide compelling evidence that the neural representation of
visual scenes is best understood as a consequence of the asso- ciative
processing in both the spatial and non-spatial
domains\citep{aminoff2015associative}.

>>>>

\citep{baumann2016functional} zu \citep{aminoff2015associative}:
% pPHC
pPHC showed increased activity when participants viewed (already familiar)
spatial configurations of meaningless shapes (regardless of their individual
identities);
% aPHC
aPHC was more active during the display of (already familiar) meaningless shapes
(regardless of their spatial configuration).
%
These findings can be interpreted as suggestive of pPHC visuospatial processes
and aPHC contextual processes \citep{baumann2016functional}.

@@

\citep{aminoff2015associative} How are scenes represented in the human brain?
Along what visual and semantic dimensions are scenes encoded in memory?
%

Hypothesis:
%
a) global spatial properties provide a basis for categorizing the neural
response patterns arising from scenes
%
b) non-spatial properties, such as single objects, also account for variance in
neural responses

%
The list of critical scene dimensions has continued to grow encompassing
properties such as geometric layout, big/small, crowded/sparse, and
three-dimensionality.
%
These dimensions may be better understood within the more general framework of
associative properties \citep{aminoff2015associative}.
%
Across both the perceptual and semantic domains, features of scene
representations are related to one another through learned
associations\citep{aminoff2015associative}.

%
We investigated whether different types of relations, all falling under the
heading of associative processing, reliably regions of brain networks known to
be scene selective\citep{aminoff2015associative}.
%
Critically, the components of such associations are consistent with the
dimensions that are typically invoked to account for scene understanding and its
neural bases\citep{aminoff2015associative}.

Results: We show that non-scene stimuli displaying novel associations across
identities or locations recruit putatively scene-selective regions of the human
brain (the parahippocampal/lingual region, the retrosplenial complex, and the
transverse occipital sulcus/occipital place area)\citep{aminoff2015associative}.

%
Moreover, we find that the voxel-wise neural patterns arising from these
associations are significantly correlated with the neural patterns arising from
everyday scenes providing evidence whether the same encoding principals underlie
both types of processing\citep{aminoff2015associative}.

%
Interpretation: Results provide evidence that the neural representation of
scenes is better understood within the broader theoretical framework of
associative processing\citep{aminoff2015associative}.
%
Results also demonstrate a division of labor that arises across scene-selective
regions when processing associations and scenes providing better understanding
of the functional roles of each region within the cortical network that mediates
scene processing\citep{aminoff2015associative}.

@@

Scenes are complex stimuli containing rich, statistically regular information
about objects, background, context, semantics, and spatial layout at multiple
scales.
%
As a core component of scene understanding we extract and learn these
regularities (certain objects typically appear together
[1–3]).
%
Associated regularities are useful in defining scene as well as in predicting
which other objects and relations are likely to occur within a scene
[5].

% a-modality
Features of any kind of mental representation, irrespective as to whether that
representation is nominally visual, linguistic, etc., are related to one another
via learned associations.
%
These associations are not necessarily modality-specific (for example, visual
representations are likely to carry many semantic and affective associations not
directly present in the image).

%
With respect to scene understanding, we construe contextual associative
processing as a more semantically-driven process in which associations are not
arbitrary relations, but rather relations that emerge as a consequence of their
shared context within the larger scene.
%
Associations are not simply frequently co-occurring features pairs; instead they
are pairs that both co-occur and add meaning to scenes.
%
Furthermore, the mechanism by which scenes are perceived, recognized, and
understood, is through means of processing the associations elicited from
components of the scene.

%
At the core of neurally-based theories of scene perception are the issues of the
computations and representations instantiated in each of these brain regions.
The literature has focused on more the representations, characterizing the
nature of the information encoded about scenes.
%
It has been suggested that scenes are analyzed in terms of their spatial global
properties, such as the ‘spatial envelope’, which takes into account a scene’s
overall spatial structure and layout [20,21].
%
Empirically, it has been demonstrated that global properties are salient
cues for categorizing scenes in both behavior [22] and in patterns of neural
activity [23–26].

%
Compared to other factors that characterize scenes (i.e., content and depth),
the expanse of the scene (i.e. its spatial boundary) has been found to be the
most effective in accounting for variations in the neural responses within
scene-selective brain regions [23,24].
%
Generally, spatial information defining the geometric layout of a scene has
often been implicated in determining the neural responses arising from
scene-selective brain regions [27].

%
In contrast, non-spatial properties can account for variations in the neural
responses associated with scene processing and
representation.
%
For example, Harel et al. [11], found that the neural encoding of scenes
captures information about single objects (i.e., non-spatial) as well as
background spatial properties.
%
Supporting this point, strongly contextualized objects also elicit neural
activity within scene-selective cortex [28,29].

%
Finally, objects present as the contents of a scene can also modulate activity
in scene-selective regions.
%
For example, scenes where the most salient object carries strong contextual
associations (e.g., a scene with a parking meter) recruit scene-selective
regions more than do scenes with a salient object carrying weak contextual
associations (e.g., a scene with a squirrel) [30].

%
Overall, scene-selective brain regions are encoding a rich collection of
information, including global and local properties, spatial background
information, and individual object tokens.

%
The list of critical properties keeps growing (e.g., big/small, crowded/sparse,
three-dimensionality [31–33]), some seemingly contradicting others about which
properties are critical in scene understanding.
%
Scene understanding may be better understood within a more general framework in
which scenes are encoded with respect to their associative properties
[28,30,34,35].
%
Associative properties are not restricted to the spatial or the global domain,
and can account for why information regarding spatial layout and single objects
play an important role in scene understanding and concomitant neural
responses.

%
Associative processing offers an explanation for what particular kinds
of information are present in scene representation (e.g., objects and spatial
information) and a basis for explaining how and why this information is
important.
%
For instance, on average, spatial layout and global properties may carry more
associative information, and thus are typically prominent in accounts of the
mechanisms mediating scene recognition.

%
To test the idea that associative processing is inherent in scene understanding,
we explore whether the network of brain regions recruited in scene perception is
also recruited when processing non-scene-like stimuli that contain associative
information.

%
If these regions are active when processing the associations learned between
non-scene-like novel stimuli than these regions must not be involved in only
processing the visual properties of the scene, but rather, are processing what
is associated with the components of the scene as learned from previous
experience.

%
We focus on the associative processing of concurrent object identities (i.e.,
semantic associations) and spatial relations between objects (i.e., spatial
associations).

%
For both semantic and spatial associations, we predict that the three
typically-identified scene-selective brain areas, the PPA, RSC, and OPA, will
all exhibit selective activity for both scenes and for associations in general,
without necessarily having any obvious “scene-like”
qualities.

%
We are positing that scene processing is best understood as, at least in part,
arising from a more general mechanism–that of associative
processing.
%
The fact that this mechanism is more general does not make it vague. Our point
is that learning and encoding relations between tokens (“associations”) is a
fundamental process across many cognitive domains and, critically, this process
has explanatory validity for scene processing.
%
Reframing scene processing as involving a more general mechanism helps
articulate the means by which scene perception
occurs.

%
Participants were scanned while they engaged in processing either everyday
scenes or associations between meaningless shapes.
%
For processing of meaningless shapes, participants performed a task (prior to
scanning; unrelated to the associations) in which they implicitly learned
spatial or identity associations between configurations of novel shapes (Fig
1).

%
First, to compare brain activity from learning novel associations to the
processing of scenes, we correlated the distributed, voxel-by-voxel pattern of
activities arising from these two conditions, thereby testing whether similar
neural mechanisms mediate both general associative processing and scene
perception.

%
Second, consistent with previous work ([28,31,34,37]) we asked whether the
neural encoding of scenes shifts across association types–from non-spatial or
semantic scene properties to spatial scene properties–as one moves from the
anterior to the posterior PPA.
%
These analyses shed light on the hypothesis that a single underlying principle,
associative processing, accounts for how scenes are represented in the
brain.

%
Although prior studies have manipulated spatial and identity associations by
having participants learn meaningless patterns of shapes [34], ours is the first
study to directly compare such associative processing with the processing of
everyday scenes.

%
We include two new baselines to better understand whereby effects of
associations arise: weak contextual objects and scrambled images. Finally, we
are careful to collect an additional independent dataset to functionally define
scene-selective regions.

%
These new conditions are all advances (in terms of explicating the processing of
scene-selection regions) relative to our earlier study in which we used the same
shapes and trained participants over a two-week period [34].
%
We also include several methodological changes: a spatial-only associative
condition was included to isolate spatial processing independently of identity
associations; and the no-association condition provides a better control in that
it now shows the same number of shapes as the association condition (i.e., 3).

@@

%
There is some evidence that within the parahippocampal region, anterior and
posterior regions may support different kinds of associations
[34,37,40,41].
%
a) aPPA processes non-spatial associations (as realized in the ID condition)
%
b) pPPA process spatial associations (as realized in the SP
condition.
%
We tested this hypothesis by examining two contrasts within scene-selective PHC
regions: SP versus NA and ID versus NA.
(we used the scenes versus baseline contrast to capture all scene-related
activity within parahippocampal cortex).

%
The pattern of average activity across subregions supports a division of labor
in which
%
a) anterior subregions showed the largest differences in the ID versus NA
contrast relative to the SP versus NA contrast, while
%
b) posterior subregions showed the largest differences in the SP versus NA
contrast relative to the ID versus NA contrast.
%
In the LH PPA this was significant in both in the interaction of Association by
Subregion (F(4,56) = 5.85, p < .001) and critically, in the linear interaction
contrast (F(1,14) = 8.05, p < .01).
%
The significance of this linear contrast indicates that the transition from
identity to spatial associative processing may be construed as a gradient from
anterior to posterior regions of parahippocampal cortex. However, the same
Association by Subregion interaction was not observed in the RH
PPA.

%
To examine whether identity and spatial associations also capture
functionally-relevant properties within scenes, we examined the similarity
between the voxel-wise pattern of BOLD responses elicited by identity
associations and real-world scenes, and by spatial associations and real-world
scenes.
%
We hypothesized that, to the degree that these two types of associations are
intrinsic to scene processing, similar patterns of activation across each of the
two association conditions and real-world scenes would identify those
(potentially separable) neural substrates supporting the representation of these
kinds of associations.

%
Unthresholded t-values for the ID versus NA and SP versus NA contrasts within
each of the five PPA subregions were extracted for each voxel and then
cross-correlated within each subregion with the real-world scenes versus
objects/scrambled contrast.
%
In LH PPA the interaction within an omnibus ANOVA [the two factors being
Subregion (moving from the most posterior to the most anteri- or) x Association
(identity or spatial)] was significant (F(4,56) = 2.69, p < .04) as well as the
critical linear x linear trend analysis (F(1,14) = 7.57, p < .016) (Fig
3A).
%
Consistent with our analysis of average activity within these subregions, this
interaction was not observed in the RH PPA (F(1,14) = 1.22, n.s.) (S1
Fig).
%
However, it is worth noting that within the right hemisphere, the correlation
between spatial associations and real-world scenes did exhibit the predicted
pattern whereby the strongest correlation was observed in posterior subregions
of PPA, with a progressively lower correlation being observed moving in a
posterior to anterior direction (S1 Fig).

%
=> Our results indicate that the organization of PPA with respect to associative
processing is a gradient in which posterior subregions of PPA are biased towards
spatial associations and anterior subregions of PPA are biased towards identity
associations.

%
Additional support for this claim is shown in Fig 3B, where instead of dividing
the PPA into five equal subregions, the correlation was run over progressively
more and more of the PPA, starting from the most posterior subregion and adding
subregions until the entire PPA was taken into account;
%
As illustrated, the most extreme ends of the PPA show the strongest biases
towards capturing the similarity of either spatial associations and scenes, or
identity associations and scenes.
%
whereas if the whole PPA were to be surveyed, these differences would be masked.
Of note, this gradient appears to be truly continuous across posterior and
anterior portions of the PPA–even considering only the posterior PPA, we observe
a gradient in which the strongest preference for spatial associations is found
in the most posterior portions of the posterior
PPA.
%
Similarly, considering only the anterior PPA, we observe a gradient in which the
strongest preference for identity associations is found in the most anterior
portions of the anterior PPA.

@@

Results suggest some specialization (at least in preference) for the processing
of associative information across the PPA.
%
pPPA is preferentially recruited by spatial associations while anterior PPA is
preferentially recruited by semantic (i.e., non-spatial) associations.

%
A functional distinction between anterior and posterior PPA has been reported
previously. In particular, this distinction has been based on PPA responses when
processing objects associated with spatial contexts (i.e., contexts associated
with specific places, for example, an oven and a kitchen) and when processing
objects associated with non-spatial contexts (i.e., contexts not tied to
specific places, for example, champagne with New Year’s Eve) [28,34,37,40,41].

%
Here, we explicitly investigated this spatial/non-spatial distinction by
isolating the two association types in simple, novel stimuli and then relating
these controlled stimuli to the processing of real-world scenes containing
similar associations.
%
We predicted that this Association-Type x Scene correlation would reveal the
expected posterior to anterior progression with spatial properties within scenes
selectively recruiting posterior PPA and non-spatial, identity properties within
scenes selectively recruiting anterior PPA.
%
Moreover, we expected that this functional division would be continuous, with
the similarity in BOLD responses elicited by scenes and trained spatial
associations decreasing in a posterior to anterior direction.
%
In contrast, the similarity in BOLD responses elicited by scenes and trained
identity associations was predicted to decrease in an anterior to posterior
direction. These predictions were confirmed in our study.

%
This information processing gradient may lie within a broader, more general
organization of the PHG.
%
The gradient of processing identity or non-spatial associative information may
continue through the neighboring perirhinal cortex, which is thought to be
involved in object and person recognition particularly with regard to combining
different fea- tures of knowledge, such as a stop sign is red
[42].
%
In contrast, the pPPA border regions where mid-level visual information is
processed, which may be more sensitive to spatial
information.
%
We do note, however, that this interaction was only observed in the left
hemisphere, although the right hemisphere demonstrated a similar gradient of
specialization in spatial processing from posterior to
anterior.

%
However, the activity related to identity processing was less well organized.
This pattern of results is somewhat consistent with the fact that the left
hemisphere is often implicated in more semantically-oriented processing, for
example, scene categorization, whereas the right hemisphere has been implicated
in more spatial processing, for example, as in the visual details between
different exemplars of the same category [10].
%
These patterns hint that the right hemisphere PPA may play a larger role in the
processing of the spatial relations within scenes and a lessor role in the
processing of scene semantics.
%
In sum, our current functional view of the PPA is as a gradient in which
progressively different scene dimensions come to be
instantiated.

@@

%
We invoke associative processing as a computationally-definable construct for
predicting the spatial organization of scene-related activity across different
scene properties.
%
we suggest that the neural mediators of scene processing should not be construed
as encapsulated visual modules, but rather as manifestations of associations
that reflect the interaction between visual recognition processes and the
application of long-term memories arising from past experiences (Aminoff et al.,
2013).
%
Within this framework, scene processing is not a purely bottom-up visual
process, but rather is an interactive process in which we are constantly
considering–in the form of both spatial and non-spatial associations– our past
experiences to generate predictions, expectations, and constraints about our
physical environment.

%
We suggest that general associative processing mechanisms are sensitive to
frequently occurring or repeated relations within scenes, including object
identities that co-occur, spatial relations between the objects, and spatial
locations for individual objects, all of which facilitate the recognition and
categorization of visual scenes.
%
As such, the collection of associations that help to define a scene provides a
context for individual elements within that scene.
%
For example, a towel hanging on a rack near a shower would most likely be a
bathroom towel, whereas the same towel lying flat on the sand near an umbrella
would most likely be a beach towel.
%
We contend that the parsing of these sorts of contextual associations within
scenes is fundamental to scene understanding, and that scene understanding
construed as such, can then influence cognitive processing in myriad
ways.

%
Within the human brain, we argue that the neural bases for the application of
contextual knowledge is a functional gradient spanning different types of
associations instantiated across the PPA, and contextually-mediated
representations within the RSC and OPA.
%
Most saliently, our observations of selectivity for spatial and identity
associations provide compelling evidence that the neural representation of
visual scenes is best understood as a consequence of the asso- ciative
processing in both the spatial and non-spatial domains.
